\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-05-05 sections/tables_figures.tex
Add: Updated parameter table for SP step

      \multirow{7}{*}{Denoising and Clustering} & \multirow{5}{*}{Denoising and Clustering} & Closed reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\

>>>>

      \multirow{7}{*}{Denoising and Clustering} & \multirow{5}{*}{Denoise and Cluster} & Closed reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
